**Implementing Simple Linear Regression in R**

Linear regression in R is accomplished with the lm() function, which stands for "linear model." Let's look at how to use a sample dataset to construct a simple linear regression.

Step 1: Data Loading and Exploration

We'll utilize a sample dataset of data for this demonstration.csv file with two variables: X as independent variable and Y as dependent variable.

```{r}
# Load the dataset
data <- read.csv("data.csv")

# View the structure of the dataset
str(data)

# Summary statistics
summary(data)

```

Step 2: Data Visualization Visualizing the data before applying linear regression aids in understanding the relationship between variables.

```{r}
# Scatter plot to visualize the relationship
plot(data$X, data$Y, main = "Scatter plot of X vs Y",
     xlab = "X", ylab = "Y", col = "blue", pch = 19)
```

Step 3: Linear Model Fit Let's now design a linear regression model based on X to predict Y.

```{r}
# Fit a linear regression model
model <- lm(Y ~ X, data = data)

# Summary of the model
summary(model)

```

Step 4: Create a Regression Line On the scatter plot, draw the regression line as follows.

```{r}
# Scatter plot with regression line
plot(data$X, data$Y, main = "Linear Regression",
     xlab = "X", ylab = "Y", col = "blue", pch = 19)
abline(model, col = "red")
```

Step 5: Making Prognoses The model can be used to forecast fresh data:

```{r}
# Create new data for prediction
new_data <- data.frame(X = c(10, 15, 20))  # Example values of X

# Predictions
predictions <- predict(model, newdata = new_data)
predictions

```

Conclusion

It is simple to implement linear regression in R, allowing us to analyze the relationship between variables, make predictions, and gain important insights from the data.
